Towards Verifying the Bitcoin-S Library

### 2019-06-21 paper/paper.tex
add more code example to BigInt to Long conversion
add stainless output

\subsection{Rewriting BigInt Comparison with Long}

Stainless output:
\begin{lstlisting}[style=stainless]
  [ Error  ] inv$4 depends on missing dependencies: long2bigInt$0.
\end{lstlisting}

@@

@@

Finally, we get some output from Stainless about the verification in the code.
\begin{lstlisting}[style=stainless]
[...]
[Warning ]  => INVALID
[Warning ] Found counter-example:
[Warning ]   thiss: { x: Object | @unchecked isNumber(x) } -> Int64Impl(0)
[Warning ]   num: { x: Object | @unchecked isInt64(x) }    -> Int64Impl(9223372036854775808)
[...]
[  Info  ] +  precond. (call checkResult(thiss, underlying(thiss) + u ...)  invalid  Code.scala:16:45
[...]
[  Info  ] total: 5  valid: 4  (4 from cache) invalid: 1  unknown: 0  time:  1.317
\end{lstlisting}

>>>>

\subsection{Rewriting BigInt to Long Conversions}

Stainless output:
\begin{lstlisting}[style=stainless]
  [ Error  ] inv$4 depends on missing dependencies: long2bigInt$0.
  [ Error  ] apply$14 depends on missing dependencies: BigInt$0, apply$15.
\end{lstlisting}

@@

And before:
\begin{lstlisting}[style=scala]
case object Int64 extends BaseNumbers[Int64] {
  lazy val zero = Int64(0)
  lazy val one = Int64(1)

  lazy val min = Int64(BigInt("-9223372036854775808"))
  lazy val max = Int64(BigInt("9223372036854775807"))

@@

Finally, we get some output from Stainless about the verification in the code.

\todo{kai special chars from stainless output what now?}
% \begin{lstlisting}[style=stainless][Warning ] The Z3 native interface is not available. Falling back onto smt-z3.
%   [  Info  ]  - Checking cache: 'adt invariant' VC for apply @33:39...
%   [  Info  ]  - Checking cache: 'adt invariant' VC for apply @62:38...
%   [  Info  ] Cache miss: 'adt invariant' VC for apply @62:38...
%   [  Info  ] Cache hit: 'adt invariant' VC for apply @33:39...
%   [  Info  ]  - Now solving 'adt invariant' VC for apply @62:38...
%   [  Info  ]  - Result for 'adt invariant' VC for apply @62:38:
%   [Warning ]  => INVALID
%   [Warning ] Found counter-example:
%   [Warning ]   bigInt: BigInt -> -9223372036854775809
%   [  Info  ]  - Checking cache: 'precond. (call checkResult(thiss, underlying(thiss) + u ...)' VC for + @17:36...
%   [  Info  ] Cache miss: 'precond. (call checkResult(thiss, underlying(thiss) + u ...)' VC for + @17:36...
%   [  Info  ]  - Now solving 'precond. (call checkResult(thiss, underlying(thiss) + u ...)' VC for + @17:36...
%   [  Info  ]  - Result for 'precond. (call checkResult(thiss, underlying(thiss) + u ...)' VC for + @17:36:
%   [Warning ]  => INVALID
%   [Warning ] Found counter-example:
%   [Warning ]   num: Number   -> Int64Impl(9223372036854775807)
%   [Warning ]   thiss: Number -> Int64Impl(1)
%   [  Info  ]   ┌───────────────────┐
%   [  Info  ] ╔═╡ stainless summary ╞══════════════════════════════════════════════════════════════════════════════════════════════════════════════════════╗
%   [  Info  ] ║ └───────────────────┘                                                                                                                      ║
%   [  Info  ] ║ +      precond. (call checkResult(thiss, underlying(thiss) + u ...)  invalid           U:smt-z3  number/NumberType.scala:17:36       0.110 ║
%   [  Info  ] ║ apply  adt invariant                                                 valid from cache            currency/CurrencyUnits.scala:33:39  1.136 ║
%   [  Info  ] ║ apply  adt invariant                                                 invalid           U:smt-z3  number/NumberType.scala:62:38       0.394 ║
%   [  Info  ] ╟┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄┄╢
%   [  Info  ] ║ total: 3    valid: 1    (1 from cache) invalid: 2    unknown: 0    time:   1.640                                                           ║
%   [  Info  ] ╚════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════════╝
%   [  Info  ] Shutting down executor service.  
% \end{lstlisting}
